### 2014-02-28 src/paper.Rnw
update

\begin{enumerate}
\item [TODO] We should check if the distribution significantly different too.
\item [TODO] Use sampling
\item [TODO] Check on randoop samples too
\item [TODO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [TODO] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}

>>>>

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [DONTKNOWHOWTO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}
